
%hi
\documentclass{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts, fancyhdr, color, comment, graphicx, environ}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage{indentfirst}
\usepackage{hyperref}
\renewcommand{\footrulewidth}{0.8pt}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}


\pagestyle{fancy}



\newenvironment{problem}[2][Problem]
    { \begin{mdframed}[backgroundcolor=gray!20] \textbf{#1 #2} \\}
    {  \end{mdframed}}


\newenvironment{solution}{\textbf{Solution}}


\lhead{Kasra Amani}
\rhead{Computer Simulation} 
\chead{\textbf{Assignment 2}}
\lfoot{Dr. Bardia Safaei}
\rfoot{Sharif University of Technology}
\def\thesection{\alph{section}}

\begin{document}
\input{coverPage}%not necessary but looks fancy
    \begin{problem}{1}
    	\textbf{Jitter:} Continuous, Dynamic and Stochastic.\\
    	\textbf{Capacitor Lifetime:} Continuous, Static and Stochastic.\\
    	\textbf{Power consumption of a switch:} Continuous, Static and Deterministic.\\
    	\textbf{Processing n packets:} Discrete, Dynamic and Deterministic.
    \end{problem}
    
    \begin{problem}{2}
    	Imagine a store clerk waiting for the next customer; the time it takes for the next customer 
    	to arrive is independent of previous customers.\\
    	Rolling a dice is also memoryless.\\
    	The time it takes for the next hardware failure to happen does not depend on 
    	previous failures and thus, it is also memoryless (this is the reason we can never predict
    	hardware failures).
    \end{problem}
    \begin{problem}{3}
    	\begin{section}{}
    		\noindent \textbf{Advantages: }can predict and avoid life threatening and dangerous 
    		situations - can speed up the passing of time and study a system's behavior in advance - 
    		Is cost effective (mostly)\\ \\
    		\textbf{Disadvantages: }Missing a (seemingly) insignificant detail in the 
    		implementation can cause devastating losses in the result - It can be expensive to 						measure environmental variables and implement the software - To simulate something 
    		a thorough and complete understanding of that subject is required
    	\end{section}
    	\begin{section}{}
    		\noindent
    		LIFO (like a stack): The advantage is the processor is sure that 
    		the latest task in the queue is what it should work on; but the disadvantage is
    		the earlier tasks can starve and never be attended to.\\ \\
    		FIFO (first come first serve): It acts fairly in the sense that if the task arrives
    		earlier it will be processed sooner, but on the flipside, tasks at the end of the queue
    		will have to wait a long time.\\ \\
    		HIFO (highest value first out): A valuing system must be designed and tasks
    		must be valued according to it; then the task with the highest value will 
    		be attended to first. The advantage is clear, since important tasks
    		will be done sooner, but on the other side, other tasks might starve.
    	\end{section}
    	\begin{section}{}
    	 	\noindent
    	 	Simulation software can be used to train new employees in an environment where
    	 	real training can be both costly and risky.\\ \\
    	 	In a business the risk-reward process in different aspects of the organization can
    	 	be simulated via a simulation software and the results can assist the board of directors
    	 	to decide the future plans of that business.
    	\end{section}
    \end{problem}
    \begin{problem}{4}
    	In the Jupyter notebook.
    \end{problem}
    \begin{problem}{5}
        In the Jupyter notebook.
    \end{problem}
    \begin{problem}{6}
        In the Jupyter notebook.
    \end{problem}

\end{document}